\documentclass{resume} % Use the custom resume.cls style
\usepackage[left=0.75in,top=0.3in,right=0.75in,bottom=0.5in]{geometry} % Document margins
\usepackage{tabularx}
\usepackage[hidelinks]{hyperref}
\name{Michael C. Micros} % Your name

%\address{Office: 2117 Engineering Systems Bldg., ODU, Norfolk, VA 23529} % Your address
%\address{Home: 7701 Enfield Ave.\  Apt \texttt{\#}204 Norfolk, VA 23505} % Your address
%\address{garett.johnson@gmail.com \\ {904\ .\ 742\ .\ 8157} }


\begin{document}

\vspace{-25 pt}
\begin{center}
757-214-2996\\
\href{mailto:mmicr001@odu.edu}{email: mmicr001@ odu.edu}\\
Github: github.com/mmicr001
\end{center}




%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}{\bf Old Dominion University} \hfill {\em Expected graduation: Dec 2017} \\ 
Major:  Computer Engineering  \\ 
Minor: Computer Science, Electrical Engineering \\
Overall GPA: 3.82/4.0
\end{rSection}


\vspace{-5 pt}


%----------------------------------------------------------------------------------------
%	RESEARCH EXPERIENCE
%----------------------------------------------------------------------------------------

\begin{rSection}{Research Experience}

\begin{rSubsection}{ Undergraduate Research Assistant}{August 2015 - Present}{}{}
\item[] \emph{Advanced Signal Processing in Engineering and Neuroscience Lab}
\item[] Research work predominantly in the field of Brain Computer Interfaces(BCI) : 
\begin{itemize}
	 \setlength\itemsep{-.5em} 
 \item Brain signal acquisition and analysis used for controlling human computer interfaces.
 \item Assisting EVMS in identifying neural processes correlated with PTSD recovery and treatment.
 \item Assisting NASA in experimental design for testing the effects of workload on attention. 
 \item Extensive use of MATLAB programming and machine learning techniques.
 \item Development in C++ and Android.
 \item Peer review of journal submissions. 
 \item Experimental design.  
\end{itemize}
\end{rSubsection}

\vspace{-5 pt}

\begin{rSubsection}{Undergraduate Researcher}{June 2017}{}{}
\item[] \emph{ Intelligent Ground Vehicle Competition (IGVC)}
\begin{itemize}
	 \setlength\itemsep{-.5em} 
	\item Captain of IGV team representing Old Dominion University at the 25th Annual Intelligent Ground Vehicle Competition (IGVC)
	\item Responsible for development of lane detection software and integration.
	\item Development in Linux with use of Python, OpenCV and ROS.
\end{itemize}
\end{rSubsection}

\end{rSection}


\vspace{-5 pt}

%----------------------------------------------------------------------------------------
%	SKILLS AND STRENGTHS
%----------------------------------------------------------------------------------------

\begin{rSection}{SKILLS \& STRENGTHS}
\begin{rSubsection}{Programming}{}{}{}
	\item[] C++, Linux, MATLAB, Python, JavaScript,  SQL(Oracle),  LaTeX, Java, Assembly, VHDL, R, Standard ML
\end{rSubsection}
\end{rSection}


\vspace{-5 pt}
%----------------------------------------------------------------------------------------
%	RELEVANT COURSEWORK
%----------------------------------------------------------------------------------------

\begin{rSection}{RELEVANT COURSEWORK}
\begin{rSubsection}{CS 450/550: DATABASE CONCEPTS}{}{}{}
	\item[] Exposure to 3 level database architecture, relational algebra, SQL and PHP
\end{rSubsection}

\begin{rSubsection}{CS 432/532: WEB SCIENCE}{}{}{}
	\item[] Extensive use of Python and Javascript for web mining, data visualization, machine learning, web archiving and collective intelligence.
\end{rSubsection}

\begin{rSubsection}{CS 350: INTRO TO SOFTWARE ENGINEERING}{}{}{}
	\item[]An exploration of the software development process, with an emphasis on the tools and techniques that support project teams (Github, Redmine, Jenkins).
\end{rSubsection}

\end{rSection}



\vspace{-5 pt}
%----------------------------------------------------------------------------------------
%	AWARDS
%----------------------------------------------------------------------------------------

\begin{rSection}{AWARDS}
	Dean's List, Academic Honors Scholarship, ODU Alumni Association Scholarship, ODU Presidential Scholarship

\end{rSection}



%----------------------------------------------------------------------------------------
\end{document}
